%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\colorlet{awesome}{awesome-red}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Sebastian}{Bate}

\position{Medical Statistician}

\mobile{07985 357150}
\email{\href{mailto:sebastiangbate@gmail.com}{\nolinkurl{sebastiangbate@gmail.com}}}
\github{sgbstats}
\linkedin{sebastianbate}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {December 2023}
    {Sebastian Bate~~~·~~~Curriculum Vitae}
  {\thepage~ of \pageref{LastPage}~}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{experience}{%
\section{Experience}\label{experience}}

\begin{cventries}
    \cventry{Junior Medical Statistician}{Manchester University NHS Foundation Trust}{Mar 2021-}{}{\begin{cvitems}
\item I have been involved in multiple studies and lead on statistical design and analysis from concept through to dissemination.
\item I support all levels of researchers from undergraduate and postgraduate students, through to clinical academics and consultants.
\item I have been responsible for reviewing the design, statistical accuracy and overall viability of Trust-sponsored research protocols prior to ethics submission in collaboration with senior statisticians.
\item I have presented my research at conferences both to technical and clinical audiences [NIHR Statistics Group Conference, 2023 (best e-poster); NHS R Community Conference, 2022; Translation Manchester, 2022 (People's Choice award)].
\item I have multiple collaborations with clinicians across the whole of MFT, The University of Manchester, and other trusts, including studies in Renal, Critical Care, Gastroenterology, Cardiology, Cystic Fibrosis, Respiratory, Oncogeriatrics, Dermatology, Oncoplastic Surgery, Physiotherapy, Maternity, Trauma Care, and ENT.
\item I have been the resident statistician for Respiratory Medicine Journal Club where I led discussions critically appraising research and providing statistical context.
\item I have given multiple talks on statistics for critical appraisal across The Trust to the prestigious Specialist Foundation Program, junior doctors and level 7+ clinical practitioners.
\item I have provided informal mentoring to a junior team member.
\item I have written teaching materials for improving statistical literacy among clinicians.
\item I have given guest lectures to undergraduates and apprentices on data literacy at Manchester Metropolitan University.
\end{cvitems}}
    \cventry{Statistician}{IQVIA}{Sep 2019-Feb 2021}{}{\begin{cvitems}
\item I worked with senior biostatistics staff on the evaluation, interpretation, and reporting of study results, including writing the analysis data reviewer’s guide for one study.
\item I quality controlled regulatory documents including CSRs, summaries of clinical efficacy and safety, prescribing information, and FDA briefing documents for large pivotal studies.
\item I assisted in developing study analysis plans, including sample size calculations and mock TFLs across multiple studies.
\item I programmed TFLs for use in CSRs across multiple studies.
\item I provided guidance and interpretation on statistical matters to medical writers and statistical programmers.
\item I gained experience in applying the principles in ICH E6 (GCP), E9 (Statistics), E9R1 (Estimands).
\end{cvitems}}
\end{cventries}

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{MMath Mathematics and Statisitcs, First Class (Hons.)}{University of Manchester}{2015-19}{}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{peer-reviewed-publications}{%
\section{Peer Reviewed Publications}\label{peer-reviewed-publications}}

\hypertarget{refs-cac9791246f9bada8c632813b37c6ec5}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-gbm}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Floyd L, Bate S, Kafagi A, et al. Risk stratification to
predict renal survival in anti-GBM disease. \emph{Journal of the
American Society of Nephrology}. 2023;34(3):505-514.
doi:\href{https://doi.org/10.1681/asn.2022050581}{10.1681/asn.2022050581}}

\leavevmode\vadjust pre{\hypertarget{ref-Batejrheum}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Bate S, Brix SR. From prediction tools to precision
medicine in antineutrophil cytoplasmic antibodyassociated vasculitis.
\emph{The Journal of Rheumatology}. 2023;50(5):583-585.
doi:\href{https://doi.org/10.3899/jrheum.230115}{10.3899/jrheum.230115}}

\leavevmode\vadjust pre{\hypertarget{ref-FI}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Vasant DH, Nigam GB, Bate S, Hamdy S, Limdi JK. The
prevalence and burden of rome IV faecal incontinence in ulcerative
colitis: A cross-sectional study. \emph{Alimentary Pharmacology \&
Therapeutics}. 2023;58(1):26-34.
doi:\href{https://doi.org/10.1111/apt.17502}{10.1111/apt.17502}}

\leavevmode\vadjust pre{\hypertarget{ref-pla2r}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Ragy O, Bate S, Bukhari S, et al. PLA2R antibody does
not outperform conventional clinical markers in predicting outcomes in
membranous nephropathy. \emph{Kidney International Reports}.
2023;8(8):1605-1615.
doi:\href{https://doi.org/10.1016/j.ekir.2023.05.019}{10.1016/j.ekir.2023.05.019}}

\leavevmode\vadjust pre{\hypertarget{ref-CSOM}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Heward E, Saeed H, Bate S, et al. Risk factors
associated with the development of chronic suppurative otitis media in
children: Systematic review and meta-analysis. \emph{Clinical
Otolaryngology}. Published online 2023.
doi:\href{https://doi.org/10.1111/coa.14102}{10.1111/coa.14102}}

\leavevmode\vadjust pre{\hypertarget{ref-oremule2023mobile}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{Oremule B, Abbas J, Saunders G, et al. Mobile audiometry
for hearing threshold assessment: A systematic review and meta-analysis.
\emph{Clinical Otolaryngology}. Published online 2023.
doi:\href{https://doi.org/10.1111/coa.14107}{10.1111/coa.14107}}

\leavevmode\vadjust pre{\hypertarget{ref-cpap}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Stokes V, Goh KY, Whiting G, et al. External validation
of a prediction model for CPAP failure in COVID-19 patients with severe
pneumonitis. \emph{Critical Care}. 2022;26(1):293.
doi:\href{https://doi.org/10.1186/s13054-022-04144-4}{10.1186/s13054-022-04144-4}}

\leavevmode\vadjust pre{\hypertarget{ref-ETP}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{Doyle R, Bate S, Devenney J, et al. Evaluating the
impact of an enhanced triage process on the performance and diagnostic
yield of oesophageal physiology studies post COVID-19. \emph{BMJ Open
Gastroenterology}. 2021;8(1):e000810.
doi:\href{https://doi.org/10.1136/bmjgast-2021-000810}{10.1136/bmjgast-2021-000810}}

\end{CSLReferences}

\hypertarget{languages-certifications}{%
\section{Languages \& Certifications}\label{languages-certifications}}

\begin{itemize}
\tightlist
\item
  R, inc. Tidyverse (Expert)
\item
  SPSS (Proficient)
\item
  SAS (Was proficient, now rusty)
\item
  SQL (Moderate)
\item
  NIHR Good Clinical Practice
\end{itemize}

\hypertarget{areas-of-interest}{%
\section{Areas of interest}\label{areas-of-interest}}

\begin{itemize}
\tightlist
\item
  Prognostic modeling
\item
  Meta-analysis
\end{itemize}

\hypertarget{personal}{%
\section{Personal}\label{personal}}

\begin{itemize}
\tightlist
\item
  I have run a 3:03:45 marathon
\item
  I have an Erdos number of 6
\item
  This CV was written in RMarkdown using \emph{\{vitae\}}
\end{itemize}


\label{LastPage}~
\end{document}
